Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/theory_results.tex
More widows I think

We now introduce some additional notation to formally discuss these results.

@@

Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$. Thus,
\begin{align*}
\mathcal{S}_T &= \begin{cases}
\mathcal{S}_G,& \text{if } T \leq 0, \\
\mathcal{S}_A,& \text{o/w}
\end{cases}\\
%--
\mathcal{R}_T(s,a) &= \begin{cases}
\mathcal{R}_G(s,a),& \text{if } T \leq 0, \\
\mathcal{R}_A(s, a),& \text{o/w}
\end{cases}\\
%--
\mcT_T(s,a,s') &= \begin{cases}
\mcT_G(s,a,s'),& \text{if }T \leq 0, \\
\underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
\mcT_A(s,a,s'),& \text{o/w}
\end{cases}\\
\end{align*}

>>>>

We first introduce some additional notation.

@@

Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of $M_G$. Thus,
\begin{align*}
\mathcal{S}_T &= \begin{cases}
\mathcal{S}_G,& \text{if } T \leq 0, \\
\mathcal{S}_A,& \text{o/w}
\end{cases}\\
%--
\mathcal{R}_T(s,a) &= \begin{cases}
\mathcal{R}_G(s,a),& \text{if } T \leq 0, \\
\mathcal{R}_A(s, a),& \text{o/w}
\end{cases}\\
%--
\mcT_T(s,a,s') &= \begin{cases}
\mcT_G(s,a,s'),& \text{if }T \leq 0, \\
\underset{{g \in G(s)}}{\sum}\left[\omega(g)\mcT_G(g, a, s')\right],& \text{if } T = 1, \\
\mcT_A(s,a,s'),& \text{o/w}
\end{cases}\\
\end{align*}
